\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[pagebackref,breaklinks,colorlinks,allcolors=blue]{hyperref}

\cvprfinalcopy % comment out for review-style version

\def\cvprPaperID{****}
\def\confName{CSE 252D}
\def\confYear{2026}

\begin{document}

\title{SafeRoute: Agentic Hazard-Aware Urban Navigation in CARLA}

\author{
Rohan Sachdeva \quad Xinwei Mai \quad Pranav Prabu \quad Rathang Pandit \\
University of California, San Diego \\
{\tt\small \{rosachdeva, xinwei, pprabu, rpandit\}@ucsd.edu}
}

\maketitle

\section{Problem}
Autonomous driving in urban environments requires decision-making under uncertainty from pedestrians, occlusions, weather, and dynamic traffic. Classical perception--planning--control pipelines perform well in structured settings but can struggle in ambiguous or rapidly changing scenes.

We study real-time, risk-aware urban navigation by designing an agentic system that interprets scenes, proposes actions, critiques its decisions, and adapts behavior within a simulated environment.

\section{Motivation}
Agentic AI systems emphasize reasoning, tool use, and iterative refinement rather than static prediction alone. Autonomous driving is a natural setting for this paradigm because navigation depends on both perception and uncertainty-aware decision-making.

Rather than building a fully end-to-end driving system, we explore a modular multi-agent driving copilot that separates scene understanding, planning, safety evaluation, and execution. This structure improves interpretability and enables controlled experimentation with different components.

\section{Background and Literature}
We use the CARLA simulator, which provides realistic urban environments, dynamic actors, configurable weather, and multi-modal sensors such as RGB, depth, and LiDAR~\cite{dosovitskiy2017carla}. CARLA enables repeatable scenarios and access to environment state, making it suitable for prototyping navigation systems.

Relevant prior work includes conditional imitation learning for end-to-end driving~\cite{codevilla2018conditional} and privileged-training approaches such as ``Learning by Cheating''~\cite{chen2019learning}. On the agentic side, frameworks such as LangGraph support graph-structured workflows with planning, critique, and tool invocation~\cite{langgraph}. We build on these ideas by introducing an agentic decision layer on top of simulator perception and control.

\section{Approach}
We design a multi-agent autonomous driving copilot in CARLA with four components:
\begin{itemize}
\setlength\itemsep{0em}
\item \textbf{Perception Agent:} summarizes the scene from sensors and nearby actors.
\item \textbf{Planning Agent:} proposes high-level actions such as continue, slow down, stop, or reroute.
\item \textbf{Safety/Critic Agent:} evaluates risk, uncertainty, and consistency of proposed actions.
\item \textbf{Execution Agent:} translates selected actions into simulator controls.
\end{itemize}

These agents interact through a structured LangGraph workflow, enabling iterative reasoning and modular tool use.

\section{Expected Outcomes}
We aim to develop a CARLA-based navigation prototype across a small set of urban scenarios with traffic and varying weather. We will provide qualitative rollouts, example decision traces, and basic metrics such as collision rate, route completion, and time-to-goal.

\section{Scope and Feasibility}
To keep the project manageable within seven weeks, we will rely on CARLA's built-in simulation and sensors, use lightweight or pretrained perception where appropriate, and focus on agent orchestration and hazard-aware decision-making rather than full-stack autonomy.

{\small
\vspace{-4pt}
\bibliographystyle{ieeenat_fullname}
\bibliography{refs}
}

\end{document}